\jaxcosmo: An End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2023-01-13 paper_OJA.tex

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$, 
J. Zuntz$^3$,\\
Y. Li$^{4,5}$,\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

@@

\affiliation{$^4$Department of Mathematics and Theory, Peng Cheng Laboratory, Shenzhen, Guangdong 518066, China}
\affiliation{$^5$Center for Computational Astrophysics \& Center for Computational Mathematics, Flatiron Institute, New York, New York 10010, USA}

@@

%%%
\section*{CRedit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration \textbf{J. Zuntz:} Investigation, Writing.

>>>>

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$, 
J. Zuntz$^3$,\\
D.~Kirkby$^4$,\\
Y.~Li$^{5,6}$,\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

@@

\affiliation{$^5$Department of Mathematics and Theory, Peng Cheng Laboratory, Shenzhen, Guangdong 518066, China}
\affiliation{$^6$Center for Computational Astrophysics \& Center for Computational Mathematics, Flatiron Institute, New York, New York 10010, USA}

@@

%%%
\section*{CRedit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration.
\textbf{J. Zuntz:} Investigation, Writing.
\textbf{D.~Kirkby:}, Software and validation for sparse linear algebra.
